\tcbset{
  annotbox/.style={
    enhanced,
    colback=black!2,
    colframe=black!35,
    boxrule=0.45pt,
    arc=2mm,
    left=3mm,
    right=3mm,
    top=2mm,
    bottom=2mm,
    boxsep=1mm,
    colbacktitle=black!8,
    coltitle=black,
    fonttitle=\bfseries\sffamily,
    attach title to upper,
    boxed title style={boxrule=0pt},
    center title,
    borderline west={1.1mm}{0pt}{black!45}
  }
}

\begin{tcolorbox}[
  annotbox,
  title=\textbf{Annotator Instructions: Realistic Query Selection}
]
\small
\setlength{\parindent}{0pt}

\begin{enumerate}[label=\arabic*., leftmargin=*, itemsep=0.35ex, topsep=0.35ex]
  \item You will be given a YouTube video, a specific moment from that video, and a list of possible text queries.
  \item Imagine the following situation:
  \begin{enumerate}[label=\alph*., leftmargin=2.2em, itemsep=0.25ex, topsep=0.25ex]
    \item You previously watched the entire YouTube video.
    \item Later, you want to find that specific moment again using a text query.
    \item You have an AI system that can locate the exact timestamp if you provide a text description of the moment.
  \end{enumerate}
  \item From the list below, choose the query you would most likely give to the AI system.
  \item You should select a natural and realistic search query.
  \item `Natural' means it sounds like something a real person would actually type.
  \item `Realistic' means it is clear and not overly long.
\end{enumerate}
\end{tcolorbox}

\input{input/query survey}


\begin{tcolorbox}[
  annotbox,
  title=\textbf{Annotator Instructions: Timestamp Selection}
]
\small
\setlength{\parindent}{0pt}

\begin{enumerate}[label=\arabic*., leftmargin=*, itemsep=0.35ex, topsep=0.35ex]
  \item You will see two candidate moments from the same YouTube video shown side by side.
  \item Watch both moments and choose the one that better captures the core content of the video.
  \item Select the option that is more representative and more informative, rather than the option that is simply longer or more eventful.
\end{enumerate}
\end{tcolorbox}

\input{input/time compare appendix}
